\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.6in]{geometry}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{hyperref}
\usepackage{bookmark}


\definecolor{bluetwo}{HTML}{3A7CA5}


\newenvironment{myenv}{\begin{adjustwidth}{0.5cm}{}}{\end{adjustwidth}}

\newcommand\tab[1][0.5cm]{\hspace*{#1}}


\begin{document}

\noindent{\huge \textbf{Aarav Rakesh}}

\smallskip
\noindent\textbf{Address:} Mumbai \tab
\textbf{Phone:} +91 9582260171 \tab
\textbf{Email:} aarav.rakesh\_ug2023@ashoka.edu.in \\
\textbf{LinkedIn:} \href{www.linkedin.com/in/aarav-rakesh-55b7661b1}{\texttt{linkedin.com/aarav-rakesh-55b7661b1}}

\bigskip
\noindent
\vspace{3pt}
{\large \textcolor{bluetwo}{PERSONAL STATEMENT}}
\vspace{3pt}
\hline
\vspace{6pt}

\begin{myenv}
\tab

As a keen student of Mathematics my outlook towards any exercise in valuation has been quantitative almost as a mandate. At my first stint in a Venture Capital firm, I learned to synthesize the numerical with the qualitative; assessing founders, ideas and sizing markets the intuitive way. I studied FinTech and Gen Z consumerism extensively, attending founder calls, interacting with incubators and making competitive outlooks almost daily. Throughout I learned at length about the Indian startup ecosystem and the key to a solid investment thesis.

\bigskip
As of now I wish to broaden my horizons into other areas such as Financial Consulting; specifically how consultants approach advising a firm which wants to transform itself, launch a new product/business line, enhance exiting lines of business and successfully guide firms and industries to financial success. I would also like to put my quantitative skills to use by applying it in valuations, audits, statistical predictors and the likes. I want to understand, through first hand exposure, asset classes as seen in the financial industry. In financial advisory and expertise, I am of the belief that depth as well as breadth is vital and I’m in pursuit of the latter.
\end{myenv}
\bigskip
\noindent
\vspace{3pt}
{\large \textcolor{bluetwo}{WORK EXPERIENCE}}
\vspace{3pt}
\hline
\vspace{6pt}

\noindent
\begin{tabularx}{\linewidth}{Xr}
\textbf{Summer Associate, Equanimity Investments VC} & \textit{May 2024 - August 2024} \\
\end{tabularx}
\begin{myenv}
\begin{itemize}
\itemsep 1mm
    \item Conducted extensive incubator outreach interacting with top IITs and IIMs.
    \item Represented the firm at startup and investor events.
    \item Produced a ‘State of FinTech’ brief with data analytic insights to explore investment opportunities.
    \item Participated in a number of founder calls to understand the VC filtering process.
    \item Prepared competitive ‘outlooks’ that were used to identify and follow through on differentiated startups.
    \item Concluded with a report on Gen Z consumer insights and consequent investment opportunities with a primary survey.
\end{itemize}
\end{myenv}

\bigskip
\noindent\vspace{3pt}
{\large \textcolor{bluetwo}{RESEARCH EXPERIENCE}}
\vspace{3pt}
\hline
\vspace{6pt}

\noindent
\begin{tabularx}{\linewidth}{Xr}
\textbf{Michigan Math and Science Scholars} & \textit{June 2021 - July 2021} \\
\end{tabularx}

\begin{myenv}
Selected Internationally (with a scholarship) to a pool of 20 students. Motivated and worked on presentations in Analysis and Topology, particularly the relations between the game of Hex and Brouwer’s Fixed Point Theorem.
\end{myenv}

\smallskip

\noindent
\begin{tabularx}{\linewidth}{Xr}
\textbf{Threshold Crossing Problem for Gaussians} & \textit{May 2022 - Feb 2023} \\
\end{tabularx}

\begin{myenv}
Multi-Armed Bandit Data problems for Large Gaussians. Worked under Professor Debapratim (UPenn) and Professor Sandeep Juneja (TIFR).
\end{myenv}

\bigskip
\noindent
\vspace{3pt}
{\large \textcolor{bluetwo}{EDUCATION AND CAMPUS INVOLVEMENT}}
\vspace{3pt}
\hline
\vspace{6pt}

\noindent
\begin{tabularx}{\linewidth}{Xr}
\textbf{International Baccalaureate Diploma, Nahar International School} & \textit{May 2021 - May 2023} \\
\end{tabularx}

\begin{myenv}
Physics, Chemistry and Mathematics AA at a Higher Level. \\
Communications Head, House Captain; Tennis and Football teams.
\end{myenv}

\smallskip

\noindent
\begin{tabularx}{\linewidth}{Xr}
\textbf{Bachelor of Science (Honours) in Mathematics, Ashoka University} & \textit{Aug 2023 - Present} \\
\end{tabularx}

\begin{myenv}
CGPA: 3.9/4. \\
Courses in Real Analysis, Statistics, Linear Algebra and Advanced Matrix Analysis. \\
Collegiate Tennis and Chess Teams, Running Club.
\end{myenv}

\bigskip
\noindent
\vspace{3pt}
{\large \textcolor{bluetwo}{SUPPLEMENTAL INFORMATION}}
\vspace{3pt}
\hline
\vspace{6pt}

\textbf{Skills:}
Financial Analysis, Accounting, Applied Mathematics, Technical and Non-Technical Writing, Data Science \tab based Modelling.

 \textbf{Languages:}
English, Hindi, Python.

 \textbf{Awards/Activities:}
Michigan Math and Science Summer Scholar; One of 25 students in a batch of 800+ to be \tab offered 100\% Merit-Cum-Means Scholarship at Ashoka University (conditionally withdrawn).

\end{document}